The role of cognateness in non-native spoken word recognition

### 2021-12-22 manuscript/manuscript.Rmd
Fix participant group

tab_loos <- model_loos %>% 
  as.data.frame() %>% 
  rownames_to_column("model") %>% 
  arrange(desc(elpd_loo)) %>% 
  select(model, matches("elpd_loo"), matches("looic"), matches("diff")) %>%
  mutate(model = str_replace(model, "fit_", "Model ")) %>% 
  mutate_all(~ifelse(. == 0, NA, .)) %>% 
  gt(rowname_col = "model") %>% 
  tab_header(
    title = md("Table 2"),
    subtitle = md("Model performance and comparison using leave-one-out cross-validation")
  ) %>% 
  tab_source_note(
    md("*Note*. Outcomes of the leave-one-out cross-validation procedure. Each row indicates the values of the expected log-predicted density (*ELPD*), leave-one-out information creterion (*LOO-IC*), and the difference in *ELPD* (*LOO-diff*) between each model and the inmediately simpler model. Each value is accompanied by a standard error (*SE*) indicating the uncertainty of its estimate.")
  ) %>% 
  fmt_missing(everything(), missing_text = "-") %>% 
  fmt_number(2:7) %>% 
  cols_label(
    model = md("**Model**"),
    looic = md("***LOO<sub>IC</sub>***"),
    se_looic = md("***SE*<sub>IC</sub>**"),
    elpd_loo = md("***LOO<sub>ELPD</sub>***"),
    se_elpd_loo = md("***SE***"),
    elpd_diff = md("***LOO<sub>diff</sub>***"),
    se_diff = md("***SE<sub>diff</sub>***")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = list(cell_borders(sides = c("left", "right"), color = "white"),
                 cell_text(align = "center")),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), 
                 cell_borders(sides = "all", color = "white")),
    locations = list(cells_stub(), cells_source_notes())
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:7)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:7)
  ) %>% 
  gtsave(here("Figures", "loos.png"))

@@

The conditional intra-class correlation (*ICC*) for items was `r percent(icc_conditional, accuracy = 0.01)`, indicating that responses from different participants to the same item were, on average, more similar to each other than responses to other items [@gelman2006data]. Item-level intercepts showed remarkable variability (*SD* = `r percent(sds$sd_word_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_word_Intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_word_Intercept$.upper, accuracy = 0.01)`]), indicating that participants' accuracy differed substantially across words: some words were correctly translated nearly always (e.g., Spanish *tomate*-*tomato*, /tomate/-/təmɑːtoʊ/, `r percent(word_example$tomate$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$tomate$q2_5, accuracy = 0.01)`, `r percent(word_example$tomate$q97_5, accuracy = 0.01)`]), while others were almost never translated correctly (e.g., Catalan *colom*-*pigeon*, /kulom/-/pɪdʒɪn/, `r percent(word_example$colom$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$colom$q2_5, accuracy = 0.01)`, `r percent(word_example$colom$q97_5, accuracy = 0.01)`]). Participant-level intercepts also showed high variability (*SD* = `r percent(sds$sd_participant_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_intercept$.upper, accuracy = 0.01)`]), suggesting that average translation accuracy also varied significantly across participants. Finally, participant-level estimated slopes showed less variability: *SD* of $Frequency$, $PTHN$, $Levenshtein$, $PTHN \times Levenshtein$, and $Levenshtein \times Group 2$ ranged between `r percent(participant_ranef_range[1], accuracy = 0.01)`, and `r percent(participant_ranef_range[2], accuracy = 0.01)`. The participant-level estimated slopes of the $Leveshtein \times Group 1$ interaction are an exception, though (*SD* = `r percent(sds$sd_participant_lv_group_en_gvs_spa$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_lv_group_en_gvs_spa$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_lv_group_en_gvs_spa$.upper, accuracy = 0.01)`]). This indicates that the impact of phonological similarity ($Levenshtein$) on the difference in accuracy between English and Spanish natives differed substantially across participants.

>>>>

tab_loos <- model_loos %>% 
  as.data.frame() %>% 
  rownames_to_column("model") %>% 
  arrange(desc(elpd_loo)) %>% 
  select(model, matches("elpd_loo"), matches("looic"), matches("diff")) %>%
  mutate(model = str_replace(model, "fit_", "Model ")) %>% 
  mutate_all(~ifelse(. == 0, NA, .)) %>% 
  gt(rowname_col = "model") %>% 
  tab_header(
    title = md("Table 2"),
    subtitle = md("Model performance and comparison using leave-one-out cross-validation")
  ) %>% 
  tab_source_note(
    md("*Note*. Outcomes of the leave-one-out cross-validation procedure. Each row indicates the values of the expected log-predicted density (*ELPD*), leave-one-out information criterion (*LOO-IC*), and the difference in *ELPD* (*LOO-diff*) between each model and the inmediately simpler model. Each value is accompanied by a standard error (*SE*) indicating the uncertainty of its estimate.")
  ) %>% 
  fmt_missing(everything(), missing_text = "-") %>% 
  fmt_number(2:7) %>% 
  cols_label(
    model = md("**Model**"),
    looic = md("***LOO<sub>IC</sub>***"),
    se_looic = md("***SE*<sub>IC</sub>**"),
    elpd_loo = md("***LOO<sub>ELPD</sub>***"),
    se_elpd_loo = md("***SE***"),
    elpd_diff = md("***LOO<sub>diff</sub>***"),
    se_diff = md("***SE<sub>diff</sub>***")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = list(cell_borders(sides = c("left", "right"), color = "white"),
                 cell_text(align = "center")),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), 
                 cell_borders(sides = "all", color = "white")),
    locations = list(cells_stub(), cells_source_notes())
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:7)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:7)
  ) %>% 
  gtsave(here("img", "loos.png"))

@@

The conditional intra-class correlation (*ICC*) for items was `r percent(icc_conditional, accuracy = 0.01)`, indicating that responses from different participants to the same item were, on average, more similar to each other than responses to other items [@gelman2006data]. Item-level intercepts showed remarkable variability (*SD* = `r percent(sds$sd_word_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_word_intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_word_intercept$.upper, accuracy = 0.01)`]), indicating that participants' accuracy differed substantially across words: some words were correctly translated nearly always (e.g., Spanish *tomate*-*tomato*, /tomate/-/təmɑːtoʊ/, `r percent(word_example$tomate$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$tomate$q2_5, accuracy = 0.01)`, `r percent(word_example$tomate$q97_5, accuracy = 0.01)`]), while others were almost never translated correctly (e.g., Catalan *colom*-*pigeon*, /kulom/-/pɪdʒɪn/, `r percent(word_example$colom$estimate, accuracy = 0.01)`, 95% CrI = [`r percent(word_example$colom$q2_5, accuracy = 0.01)`, `r percent(word_example$colom$q97_5, accuracy = 0.01)`]). Participant-level intercepts also showed high variability (*SD* = `r percent(sds$sd_participant_intercept$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_intercept$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_intercept$.upper, accuracy = 0.01)`]), suggesting that average translation accuracy also varied significantly across participants. Finally, participant-level estimated slopes showed less variability: *SD* of $Frequency$, $PTHN$, $Levenshtein$, $PTHN \times Levenshtein$, and $Levenshtein \times Group 2$ ranged between `r percent(participant_ranef_range[1], accuracy = 0.01)`, and `r percent(participant_ranef_range[2], accuracy = 0.01)`. The participant-level estimated slopes of the $Leveshtein \times Group 1$ interaction are an exception, though (*SD* = `r percent(sds$sd_participant_lv_group_en_gvs_spa$.value, accuracy = 0.01)`, 95% CrI = [`r percent(sds$sd_participant_lv_group_en_gvs_spa$.lower, accuracy = 0.01)`, `r percent(sds$sd_participant_lv_group_en_gvs_spa$.upper, accuracy = 0.01)`]). This indicates that the impact of phonological similarity ($Levenshtein$) on the difference in accuracy between English and Spanish natives differed substantially across participants.
